---
title: "initial scrape of governments"
author: "Stefan Haußner"
date: "12 Mai 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rvest)
library(janitor)
```


This script scrapes all government members from official or nonofficial webpages. The final lists should contain Name, Portfolio and the party s*he is affiliated to.

# Austria




# Belgium

Source with party affiliations: https://en.wikipedia.org/wiki/Federal_Government_of_Belgium
Official source: https://www.foderale-regierung.be/de

```{r}
url <- "https://en.wikipedia.org/wiki/Federal_Government_of_Belgium"

html <- read_html(url)
ministers_nl <- html %>% 
  html_node(".wikitable") %>% 
  html_table(fill = TRUE) %>% 
  clean_names() %>% 
  select(name = minister_2, everything(), -contains("na"), -minister) %>% 
  filter(!grepl("Minister", name)) %>% 
  mutate(name = str_remove(name,"[:blank:]\\[.*\\]"),
         cntry = "NL")

ministers_nl %>% tbl_df()
```


# Bulgaria

Source with party affiliation: https://en.wikipedia.org/wiki/Government_of_Bulgaria
Official source: https://www.gov.bg/en/Cabinet/CABINET-MEMBERS

```{r}
url <- "https://en.wikipedia.org/wiki/Government_of_Bulgaria"
html <- read_html(url)

ministers_bg <- html %>% 
  html_node(".toccolours") %>% 
  html_table(fill = TRUE) %>% 
  clean_names() %>% 
  tbl_df() %>% 
  select(name = na, portfolio = ministry_2, party = na_2) %>% 
  mutate(cntry = "BG")

ministers_bg

```


# Croatia
# Cyprus
# Czech Republic
# Denmark

Source with party affiliation: https://www.thedanishparliament.dk/en/members/the-government
Official Source: https //www.thedanishparliament.dk/en/members/the-government


```{r}
url <- "https://www.thedanishparliament.dk/en/members/the-government"
html <- read_html(url)

name <- html %>% 
  html_nodes(".cellPic+ td") %>% 
  html_node("a") %>% 
  html_text()

ministers_dk <- html %>% 
  html_nodes(".cellPic+ td") %>% 
  html_text() %>% 
  tbl_df() %>% 
  separate(value, into = c("x","portfolio","party","y","z"), sep = "\r\n") %>% 
  mutate(name = name,
         portfolio = str_remove(portfolio, name),
         cntry = "DK") %>% 
  select(name, portfolio, party, cntry)

ministers_dk
  
```

# Estonia

Source with party affiliation: https://en.wikipedia.org/wiki/J%C3%BCri_Ratas%27_second_cabinet
Official source: https://www.hm.ee/en


```{r}
url <- "https://en.wikipedia.org/wiki/J%C3%BCri_Ratas%27_second_cabinet"
html <- read_html(url)

ministers_ee <- html %>% html_node(".wikitable") %>% 
  html_table(fill = TRUE) %>% 
  clean_names() %>% 
  tbl_df() %>% 
  select(portfolio, name = minister_2, took_office, left_office, party) %>% 
  filter(!grepl(name, pattern = "Ministry"), !grepl(name, pattern = "Office")) %>% 
  mutate(name = str_remove(name,"\\[.*\\]"),
         cntry = "EE")

ministers_ee
```


# Finland

Source with party affiliation: https //valtioneuvosto.fi/en/marin/ministers
Official source: https://valtioneuvosto.fi/en/marin/ministers

```{r}
url <- "https://valtioneuvosto.fi/en/marin/ministers"
html <- read_html(url)

name <- html %>% html_nodes("#layout-column_column-5 .name") %>% html_text()
portfolio <- html %>% html_nodes(".title") %>% html_text()
links <- html %>% 
  html_nodes(".minister-tile") %>% 
  html_node("a") %>% 
  html_attr("href") %>% 
  paste0("https://valtioneuvosto.fi",.)

f_getparty <- function(link){
  p <- read_html(link) %>% html_node(".text p") %>% html_text()
  return(p)
}

ministers_fi <- bind_cols(portfolio = portfolio, name = name,  links = links) %>% 
  mutate(party = map_chr(links, f_getparty),
         cntry = "FI") %>% 
  select(-links)

ministers_fi
```


# France

Source with party affiliation: https://en.wikipedia.org/wiki/Second_Philippe_government
Official Source: https://www.gouvernement.fr/en/composition-of-the-government

```{r}
url <- "https://en.wikipedia.org/wiki/Second_Philippe_government"
html <- read_html(url)

ministers_fr <- html %>% 
  html_nodes(".wikitable") %>% 
  .[[4]] %>% 
  html_table(fill = TRUE) %>% 
  clean_names() %>% 
  tbl_df() %>% 
  filter(party == "") %>%
  mutate(cntry = "FR") %>% 
  select(portfolio = post, name = name, party = party_2)

ministers_fr

```



# Germany

```{r}

```


# Greece
# Hungary
# Ireland
# Italy
# Latvia
# Lithuania
# Luxembourg
# Malta
# Netherlands
# Poland
# Portugal
# Romania
# Slovakia
# Slovenia
# Spain
# Sweden 